\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

	\header{Rafał}{Podkoński}{Senior Developer} % Your name and current job title/field
	
	\begin{aside}
		%----------------------------------------------------------------------------------------
		%	CONTACT
		%----------------------------------------------------------------------------------------
		\section{Contact}
		Wiktorów
		ul. Stołeczna 96
		05-083 Zaborów
		Poland
		~
		\phone{(+48) 511-548-637}
		\email{rafal.podkonski@dev-software.pl}
		~
		\linkedin{rafał-podkoński}{952339137}
		\facebook{rafal.podkonski}
		\github{s13302}
		
		%----------------------------------------------------------------------------------------
		%	LANGUAGES
		%----------------------------------------------------------------------------------------
		\section{Languages}
		\rating{Polish}{5}{5}
		\rating{English}{5}{4}
		\rating{Russian}{5}{2}
		\rating{Spanish}{5}{1}
		\rating{Dutch}{5}{1}
	\end{aside}
	
	%----------------------------------------------------------------------------------------
	%	WORK SUMMARY
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Professional Summary}
		I am experienced Java programmer. I have about 6 years of experience in professional programming. I am interested in software architecture and this is the direction which I want to develop myself. I would like to extend my knowledge about Domain Driven Design, especially usage this technique in real project.
	\end{absolutelynopagebreak}
	
	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Experience}
		\begin{entrylist}
			%------------------------------------------------
			\entry
			{since July 2017}
			{Sollers Consulting Sp. z o.o.}
			{st Koszykowa 54, Warszawa}
			{\emph{Senior Developer}\\
				Business processes implementation on Guidewire suite for customers around the world. IntelliJ Sonar plugin customization for support of Gosu language.
			}
			%------------------------------------------------
			\entry
			{since March 2015}
			{Koło Naukowe Programistów Java}
			{st Koszykowa 86, Warszawa}
			{\emph{President, Mentor}\\
				Managing of science club and managing of mentors team. Programming lectures and workshops organization. Teaching students programming in Java on various levels (basic, advanced).
			}
			%------------------------------------------------
			\entry
			{June 2014-July 2017}
			{Innotion Sp. z o.o.}
			{st Łucka 2/4/6, Warszawa}
			{\emph{Developer}\\
				Creating of new solutions, maintaining of existing solutions for customers.
			}
		\end{entrylist}
	\end{absolutelynopagebreak}
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Education}
		\begin{entrylist}
			%------------------------------------------------
			\entry
			{since 2014}
			{Polish-Japanese Academy of Information Technology}
			{Koszykowa 86, Warszawa}
			{\emph{Field of study:} Computer Science\\
			\emph{Specialization:} Programowanie Aplikacji Biznesowych}
			%------------------------------------------------
			\entry
			{2011-2014}
			{University of Cardinal Stefan Wyszyński}
			{Wóycickiego 1/3, Warszawa}
			{\emph{Field of study:} Computer Science}
			%------------------------------------------------
			\entry
			{2007-2011}
			{Technikum Mechatroniczne nr 1 w Warszawie}
			{Wiśniowa 56, Warszawa}
			{\emph{Field of study:} IT Specialist\\
			\emph{Specialization:} Computer systems and networks according to the CISCO CCNA program}
		\end{entrylist}
	\end{absolutelynopagebreak}
	
	%----------------------------------------------------------------------------------------
	%	CERTIFICATES
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Certificates}
		\begin{entrylist}
			%------------------------------------------------
			\cert
			{January 2019}
			{Guidewire InsuranceSuite Integration 10.0}
			%------------------------------------------------
			\cert
			{December 2018}
			{Guidewire InsuranceSuite Integration 9.0}
			%------------------------------------------------
			\cert
			{August 2017}
			{Guidewire PolicyCenter 9.0 Configuration}
			%------------------------------------------------
			\cert
			{May 2009}
			{ECDL Certificate}
			%------------------------------------------------
			\cert
			{April 2010}
			{Driving license cat. B}
		\end{entrylist}
	\end{absolutelynopagebreak}
	
	%----------------------------------------------------------------------------------------
	%	PROJECTS
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Projects}
		\begin{entrylist}
			%------------------------------------------------
			\entry
			{since 04.2020}
			{Registration and handling system for OTOZ Animals purposes}
			{Java EE, Spring Framework, Spring Data, Hibernate, PostgreSQL, Angular 6}
			{System for registering and handling events. System allows registering issued recommendations and found animals and theirs state.}
			%------------------------------------------------
			\entry
			{since 04.2020}
			{Voting system for ESN}
			{Node.JS, ExpressJS, Socket.IO, ReactJS, PostgreSQL, MongoDB, RWD}
			{System for support voting in ESN. The key requirement for system was realtime work and working on smartphone without any external application installation.}
			%------------------------------------------------
			\entry
			{06.2016-07.2016}
			{Registration system for pilgrims groups during World Youth Days in Poland}
			{Java EE, Spring, Spring Data, Angular JS}
			{System for supporting pilgrims group registration for museums and trains. System was commissioned by the Archdiocese of Warsaw.}
			%------------------------------------------------
			\entry
			{02.2013-04.2013}
			{Exports parser from Agencja 3000 program}
			{PHP, PostgreSQL}
			{Export parser in XML format, data loaded into the PostgreSQL database and then to the estate agency's website.}
		\end{entrylist}
	\end{absolutelynopagebreak}
	
	%----------------------------------------------------------------------------------------
	%	COURSES
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Courses}
		\begin{entrylist}
			%------------------------------------------------
			\cert
			{2019}
			{Droga Nowoczesnego Architekta}
			%------------------------------------------------
			\cert
			{2011}
			{CISCO CCNA}
		\end{entrylist}
	\end{absolutelynopagebreak}
	
	%----------------------------------------------------------------------------------------
	%	INTERESTS
	%----------------------------------------------------------------------------------------
	\begin{absolutelynopagebreak}
		\section{Interests}
		\textbf{Professional: } webpage creation, software creation, application architecture, Domain Driven Design, Test Driven Design, Scrum\\
		\textbf{Personal: } cycling, ice hockey, tennis
	\end{absolutelynopagebreak}
	
	\vfill
	\textit{Wyrażam zgodę na przetwarzanie moich danych osobowych zawartych w mojej ofercie pracy dla potrzeb niezbędnych do realizacji procesu rekrutacji zgodnie z Ustawą z dn. 29.08.1997 roku o ochronie danych osobowych. Przysługuje mi prawo dostępu do treści swoich danych oraz ich poprawiania.}
	
	\begin{pside}
		%----------------------------------------------------------------------------------------
		%	PROGRAMMING LANGUAGES
		%----------------------------------------------------------------------------------------
		\section{Programming}
		\subsection{Backend}
		\rating{Java}{5}{4}
		\rating{Spring Framework}{5}{3}
		\rating{Guidewire Suite}{5}{3}
		\rating{Node.JS}{5}{2}
		\rating{Socket.IO}{5}{2}
		\rating{ExpressJS}{5}{2}
		\rating{PHP}{5}{2}
		\rating{Wordpress}{5}{2}
		
		\subsection{Frontend}
		\rating{HTML}{5}{4}
		\rating{JavaScript}{5}{4}
		\rating{Angular.JS}{5}{3}
		\rating{CSS3}{5}{3}
		\rating{Angular 2+}{5}{3}
		\rating{ReactJS}{5}{2}
		\rating{Vue.js}{5}{1}
		
		\subsection{Databases}
		\rating{PostgreSQL}{5}{3}
		\rating{Oracle}{5}{2}
		\rating{MSSQL}{5}{2}
		\rating{MongoDB}{5}{1}
		
		\subsection{Others}
		\rating{\LaTeX}{5}{3}
	\end{pside}

\end{document}